False Positive Probabilities for all Kepler Objects of Interest: \\ \nvalnew\ newly validated planets and \nfpnew\ likely false positives

### 2015-09-01 ms.tex
added mcmc table; a few edits

\begin{abstract}
We present the results of applying a fully automated transit signal
false positive probability calculating procedure to every
\kepler\ Object of Interest (KOI)---the first large-scale
demonstration of a fully automated transiting planet validation
procedure.  Out of \ncalc\ KOIs, we determine that \nval\ have
probabilities $<$1\% to be astrophysical false positives, and thus may
be considered validated planets.  \nvalnew\ of these have not yet been
validated or confirmed by other methods.  In addition, we identify
\nfpnew\ KOIs likely to be false positives that have not yet been
identified as such, though some of these may be a result of
unidentified transit timing variations. A side product of these
calculations is full stellar property posterior samplings for every
host star, modeled as single, binary, and triple systems.  These
calculations use \vespa, a publicly available Python package able to
be easily applied to any transiting exoplanet candidate.
\end{abstract}

@@

The reliability of these calculations is dependent largely on the
results of \citet{Bryson:KSCI}, which quantify the probability that
the eclipse/transit signal is spatially coincident on the sky with the
presumed target star.  Without confirmation that the transit signal is
not coming from a significantly displaced source, the sky area used as
part of the prior for the false positive scenarios would need to be
significantly larger than the positional uncertainty value assumed in
this work (described in \sect{methods:fpp}).  Additionally, the
blended false positive scenarios being considered are assumed to be
fully contained within the photometric aperture; this assumption would
also be broken if the source of the eclipse were significantly
displaced.

While previous \emph{a priori} false positive rate estimates
\cite{Morton:2011b,Fressin:2013} have made clear that the
\kepler\ planet candidate catalogs are \emph{generally} low enough to
ignore for the purposes of planet occurrence rate calculations, any
more detailed study of any small subset of individual KOIs must
understand in more detail the FPPs of those specific candidates.  This
type of small-sample candidate culling using individually calculated
FPPs has already been done in the literature
\citep{MortonSwift:2014,MortonWinn:2015}; the publication of this full
catalog allows the community to do the same.

>>>>

\begin{abstract}
We present transit signal false positive probability calculations for
every \kepler\ Object of Interest (KOI)---the first large-scale
demonstration of a fully automated transiting planet validation
procedure.  Out of \ncalc\ KOIs, we determine that \nval\ have
probabilities $<$1\% to be astrophysical false positives, and thus may
be considered validated planets.  \nvalnew\ of these have not yet been
validated or confirmed by other methods.  In addition, we identify
\nfpnew\ KOIs likely to be false positives that have not yet been
identified as such, though some of these may be a result of
unidentified transit timing variations. A side product of these
calculations is full stellar property posterior samplings for every
host star, modeled as single, binary, and triple systems.  These
calculations use \vespa, a publicly available Python package able to
be easily applied to any transiting exoplanet candidate.
\end{abstract}

@@

The reliability of these calculations is dependent largely on the
results of \citet{Bryson:KSCI}, which quantify the probability that
the eclipse/transit signal is spatially coincident on the sky with the
presumed target star.  Without confirmation that the transit signal is
not coming from a significantly displaced source, the sky area used as
part of the prior for the false positive scenarios would need to be
significantly larger than the positional uncertainty value assumed in
this work (described in \sect{methods:fpp}).  Additionally, the
blended false positive scenarios \vespa\ considers are assumed to be
fully contained within the photometric aperture; this assumption would
also be broken if the source of the eclipse were significantly
displaced.

While previous \emph{a priori} false positive rate estimates
\cite{Morton:2011b,Fressin:2013} have made clear that the
\kepler\ planet candidate catalogs are generally low enough to
ignore for the purposes of planet occurrence rate calculations, any
more detailed study of any small subset of individual KOIs should
understand in more detail the FPPs of those specific candidates.  This
type of small-sample candidate culling using individually calculated
FPPs has already been done in the literature
\citep{MortonSwift:2014,MortonWinn:2015}; the publication of this full
catalog allows the community to do the same.
